A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-06-25 src/paper.tex
Overview figure changed

The architecture presented in this paper applies to the capture of audience interactions by means of the use of second screen devices in interactive TV environments. Personal devices are used as second screen devices to enrich the interactivity between viewers and TV at the same time that they allow the capture of viewers' interactions.

\begin{figure}[!t]
	\centering
	\includegraphics[width=3.5in]{img/architecture.pdf}
	\caption{Architecture to capture audience interactions. The viewers' interactions and the contextual information are captured and stored in the CP infrastructure.}
	\label{fig_architecture}
\end{figure}

>>>>

The architecture presented in this paper applies to the capture of audience interactions by means of the use of second screen devices in interactive TV environments. Personal devices are used as second screen devices to enrich the interactivity between viewers and TV at the same time that they facilitate the capture of viewers' interactions.

\begin{figure}[!t]
	\centering
	\includegraphics[width=3.5in]{img/architecture-overview.pdf}
	\caption{Architecture to capture audience interactions. The viewers' interactions and the contextual information are captured and stored in the CP infrastructure.}
	\label{fig_architecture}
\end{figure}
